R Notebook

### 2021-09-19 documentation_and_analysis/draftbook.Rmd
Charger geo spatial

```{r}
library(tidyverse)
library(janitor)
library(readODS)
library(httr)
library(here)
library(data.table)
library(sf)
library(leaflet)
library(leaflet.extras)
```

```{r}
read_ods(here("raw_data/electric-vehicle-charging-device-statistics-june-2021.ods"))
```

```{r}
getwd()
```

```{r}
APE <- read_ods("raw_data/APE_site_data_tables.ods", sheet = 2)
```

```{r}
NO2 <- read_ods("raw_data/NO2_tables.ods")
```

```{r}
registry <- GET("http://chargepoints.dft.gov.uk/api/retrieve/registry/format/csv/") %>% 
  content()
```

```{r}
type <- GET("http://chargepoints.dft.gov.uk/api/retrieve/type/format/csv/") %>% 
  content()
```

```{r}
read_csv("Documents/GitHub/ev_climate_change_project/raw_data/no2_by_grid_2019.csv")
```

```{r}
air_pollution_cap <- GET("https://uk-air.defra.gov.uk/data/sos/service?service=AQD&request=GetCapabilities")
```

```{r}
air_pollution_cap <- rbindlist(air_pollution$content, fill = TRUE)
```

```{r}
air_pollution_cap <- unnest(air_pollution_cap)
```

```{r}
air_pollution <- GET("https://uk-air.defra.gov.uk/data/sos/service?service=SOS&version=2.0.0&request=GetObserved&observedProperty=http://dd.eionet.europa.eu/vocabulary/aq/pollutant/8") %>% 
  content()
```

```{r}
air_pollution$exceptions
```

```{r}
air_pollution <- rbindlist(air_pollution$exceptions, fill = TRUE) 
```

```{r}
air_pollution <- unnest(air_pollution)
```

# How many electric vehicles are on the road across the UK by LA?

```{r}
# Reading in and skipping first 5 rows
uk_ev <- read_ods(here("raw_data/ev_by_la.ods"), sheet = 2, skip = 5)
# Making row 1 the variable name
names(uk_ev) <- uk_ev[1,] 
# Removing row 1 
uk_ev <- uk_ev[-1,] %>% 
  clean_names()
```

```{r}
# loading in shape file 
uk_shape_file <- st_read(here("raw_data/Local_Authority_Districts__April_2019__UK_BFE_v2-shp/Local_Authority_Districts__April_2019__UK_BFE_v2.shp")) %>%
  clean_names() %>% 
  st_simplify(dTolerance = 1000) %>%
  st_transform("+proj=longlat +datum=WGS84") %>% 
  select(lad19cd, long, lat, geometry) 
```

```{r}
# Joining uk_ev + shape file 
uk_ev_map <- uk_ev %>% 
  left_join(uk_shape_file, by = c("ons_la_code_apr_2019" = "lad19cd")) %>% 
  drop_na() %>% 
  mutate(across(c(x2021_q1:x2011_q4), as.numeric)) %>% 
  st_as_sf()
```

@@

leaflet() %>%
  addProviderTiles("CartoDB.Positron", options = providerTileOptions(noWrap = TRUE)) %>%
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addHeatmap(data = no2_diff_final,
             lng = ~lon,
             lat = ~lat,
             intensity = ~no2_diff_2014_2019,
             minOpacity = 0.1,
             max = 30,
             radius = 1,
             blur = 1) %>% 
  addLegend(pal = pal, values = no2_diff_final$no2_diff_2014_2019,
                title="Average NO2 Diff")
```

@@

>>>>

```{r}
library(janitor)
library(readODS)
library(httr)
library(here)
library(data.table)
library(sf)
library(leaflet)
library(leaflet.extras)
library(tidyverse)
```

```{r}
# loading in shape file 
uk_shape_file <- st_read(here("raw_data/LA_shape/Local_Authority_Districts__April_2019__UK_BFE_v2.shp")) %>%
  clean_names() %>% 
  st_simplify(dTolerance = 1000) %>%
  st_transform("+proj=longlat +datum=WGS84") %>% 
  dplyr::select(lad19cd, long, lat, geometry) 
```

```{r}
# Load in clean Electric Vehicles by Local Authority data
uk_ev <- read_csv(here("clean_data/ev_by_la_clean.csv"))
# Joining uk_ev + shape file 
uk_ev_map <- uk_ev %>% 
  left_join(uk_shape_file, by = c("ons_la_code_apr_2019" = "lad19cd")) %>% 
  drop_na() %>% 
  mutate(across(c(x2021_q1:x2011_q4), as.numeric)) %>% 
  st_as_sf()
```

```{r}
# Set colours and bins
pal <- colorBin("Greens", domain = uk_ev_map$x2021_q1, bins = c(0, 500, 1000, 2500, 5000, 10000, 15000))

# Set labels
uk_ev_map_labels <- sprintf(
  "<strong>%s</strong><br/>%g Electric Vehicles",
  uk_ev_map$region_local_authority_apr_2019_3, uk_ev_map$x2021_q1) %>% 
  lapply(htmltools::HTML)
```

@@

leaflet() %>%
  addProviderTiles("CartoDB.Positron", options = providerTileOptions(noWrap = TRUE)) %>%
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addHeatmap(data = no2_diff_final,
             lng = ~lon,
             lat = ~lat,
             intensity = ~no2_diff_2014_2019,
             minOpacity = 0.1,
             max = 30,
             radius = 1,
             blur = 2) %>% 
  addLegend(pal = pal, values = no2_diff_final$no2_diff_2014_2019,
                title="Annual Mean NO2 Change between 2014 and 2019")
```

@@

```{r}
ev_charging <- read_csv(here("raw_data/electric-vehicle-charging-device-statistics-july-2021/EVCD_02-Table 1.csv"), skip = 6) %>% 
  clean_names() %>% 
  dplyr::select(year, month, total_devices, rapid_devices) %>% 
  filter(rapid_devices != "NA") %>% 
  mutate(total_devices = as.numeric(total_devices),
         other_devices = total_devices - rapid_devices) %>% 
  select(-total_devices) %>% 
  pivot_longer(cols = c(other_devices, rapid_devices), names_to = "charger", values_to = "number_of_chargers") %>% 
  filter(month == "October" | month == "July" & year == "2021") %>% 
  mutate(charger = factor(charger, levels = c("rapid_devices", "other_devices")))
```

```{r}
ev_charging %>% 
  ggplot() +
  aes(x = year, y = number_of_chargers, fill = charger) +
  geom_col() +
  scale_y_continuous(breaks = seq(0, 30000, 2500)) +
  coord_flip() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.5, hjust=1)) +
  scale_fill_manual(labels = c("Rapid Charger", "Standard Charger"), values = c("#e41a1c", "#4daf4a")) +
  labs(title = "\nNumber of Electric Vehicle Chargers Growth in the UK\n",
       x = "\nYear\n",
       y = "\nNumber of Chargers\n",
       fill = "Charger Type")
```

```{r}
ev_charging_rapid <- read_csv(here("raw_data/electric-vehicle-charging-device-statistics-july-2021/EVCD_01b-Table 1.csv"), skip = 6) %>% 
  clean_names() %>% 
  select(la_region_code, local_authority_region_name, jul_21) %>% 
  rename("count_rapid" = jul_21) 
ev_charging_total <- read_csv(here("raw_data/electric-vehicle-charging-device-statistics-july-2021/EVCD_01a-Table 1.csv"), skip = 6) %>% 
  clean_names() %>% 
  select(la_region_code, local_authority_region_name, jul_21) %>% 
  rename("count_total" = jul_21)

ev_charging_geo <- inner_join(ev_charging_rapid, ev_charging_total, by = "la_region_code") %>% 
  drop_na() %>% 
  select(la_region_code, local_authority_region_name.x, count_rapid, count_total) %>% 
  filter(str_detect(local_authority_region_name.x, "[a-z][a-z]")#,
         #count_rapid != "-") %>% 
  mutate(local_authority_region_name.x = str_remove_all(local_authority_region_name.x, "[(](Met County)[)]"))
```

```{r}
# Joining ev_charging_geo + shape file 
ev_charging_map <- ev_charging_geo %>% 
  left_join(uk_shape_file, by = c("la_region_code" = "lad19cd")) %>% 
  drop_na() %>% 
  mutate(across(c(count_rapid:count_total), as.numeric)) %>% 
  st_as_sf()
```

```{r}
# Set colours and bins
pal <- colorBin("Reds", domain = ev_charging_map$count_total, bins = c(0, 50, 100, 250, 500, 750, 1000, 1250))

# Set labels
ev_charging_map_labels <- sprintf(
  "<strong>%s</strong><br/>%g Chargers",
  ev_charging_map$local_authority_region_name.x, ev_charging_map$count_total, ev_charging_map$count_rapid) %>% 
  lapply(htmltools::HTML)
```

```{r}
# Geospatial of EV Vehicles in the UK 2021 Q1
ev_charging_map %>% 
  leaflet() %>% 
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(fillColor = ~pal(count_total),
    weight = 0.1,
    opacity = 0.9, 
    color = "black",
    fillOpacity = 0.8,
    highlightOptions = highlightOptions(color = "green", weight = 2,
                                        bringToFront = TRUE),
    label = ev_charging_map_labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>% 
  addLegend(pal = pal, values = ~count_total, opacity = 0.7, title = NULL,
            position = "bottomright")
```

```{r}
ev_charging_map %>% 
  filter(count_total > 500)
```
